\begin{rSection}{PROJECTS}
\vspace{-1.25em}

\item \textbf{RISC-V Digit Classifier (UCB/CS61C)} 
\begin{itemize}
    \item Built a digit classifier with RISC-V as a class project with pre-trained matrices. 
    \item Familiar with calling convention, calling functions, using the heap, interacting with files, testings and debugging RISC-V code via classroom's built-in debugger.
\end{itemize}


\item \textbf{2D Tile-Based World Exploration Generator (UCB/CS61B)} Implementing a 2D World Generator/Game that allows users/gamers to explore and interact with their surroundings. Using Java's OOP programming paradigm, git version control, and collaborating with one teammate to work on a complex codebase from scratch.

\item \textbf{Compiler with Rust} Building a compiler for a language in Rust that can emits RISC-V backend. Currently working on lexer and parser.

\item \textbf{Scheme Interpreter (UCB/CS61A)} { Built a scheme interpreter (a Lisp dialect) in Python as Berkeley's CS61A project. Used Python's OOP programming paradigm and incorporated other ideas learned in CS61A such as functional programming and recursion. Implemented tail recursion via trampolining, enabling more efficient recursive calls.
}

\item \textbf{Girls-In-Tech Hackathon Participant } Quickly learned the basics of Javascript, React, React-native, and Firebase to build a proof-of-concept iOS app designed for recycling with 3 more Berkeley students. 

\item \textbf{\href{https://github.com/badumbatish/BigInt}{Big Integer C++ }} {Utilized STL vector data structure to simulate big integers of size $>$ $2^{64}$ for addition, subtraction, and multiplication. Used Travis CI for continuous integration. Unit-tested with Catch2. Memory-profiled with Valgrind.}


\item \textbf{Trees in C++ } Implemented different querying data structures such as a \href{https://github.com/badumbatish/suffix_tree}{binary tree}, \href{https://github.com/badumbatish/trie}{trie}, \href{https://github.com/badumbatish/suffix_tree}{suffix tree}, and \href{https://github.com/badumbatish/Meep}{Meep} (hashmap + binary heap) in C++.



% \subimport{}{math_directed_mentee}
\end{rSection} 